An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/2.minbigul.tex
add labels to sections
small fixes

\section{Bidirectional Programming Language: minBiGUL}

@@

BiGUL is well-behaved [?] since two functions $\putbxinline{bx}$ and $\getbxinline{bx}$ satisfy the round-trip laws as follows:

@@

The \textsc{GetPut} \cite{Pacheco:2014:MCP:2543728.2543737} law means that if there is no change to the view, there should be no change to the source. The \textsc{PutGet} \cite{Pacheco:2014:MCP:2543728.2543737} law means that we can recover the modified view by applying the forward transformation to the updated source.

@@

\begin{multicols}{2}
    \begin{definition}
        $\putbx{bx}{s}{v}$

@@

        \noindent $\putbx{bx_1 \circ bx_2}{s}{v} = \\
            \tab \putbx{bx_1}{s}{(\putbx{bx_2}{(\getbx{bx_1}{s})}{v})}$
    \end{definition}
\columnbreak
    \begin{definition}
        $\getbx{bx}{s}$

@@

We define the semantics of $put$ and $get$ as in definitions 1 and 2 respectively. Instead of using $v'$ in the $put$ direction like figures \ref{fig:eval-phead}, \ref{fig:eval-comp-phead} and \ref{fig:eval-comp-phead-2}, we just simply use notation $v$ as the updated view. The later definitions also follow this convention.

>>>>

\section{Bidirectional Programming Language: minBiGUL} \label{sect:minbigul}

@@

BiGUL is well-behaved \cite{Pacheco:2014:MCP:2543728.2543737} since two functions $\putbxinline{bx}$ and $\getbxinline{bx}$ satisfy the round-trip laws as follows:

@@

The \textsc{GetPut} law means that if there is no change to the view, there should be no change to the source. The \textsc{PutGet} law means that we can recover the modified view by applying the forward transformation to the updated source.

@@

\begin{multicols}{2}
    \begin{definition} \label{def:minbigulput}
        $\putbx{bx}{s}{v}$

@@

        \noindent $\putbx{bx_1 \circ bx_2}{s}{v} = \\
            \tab \putbx{bx_1}{s}{(\putbx{bx_2}{(\getbx{bx_1}{s})}{v})}$
    \end{definition}
\columnbreak
    \begin{definition} \label{def:minbigulget}
        $\getbx{bx}{s}$

@@

We define the semantics of $put$ and $get$ as in Definitions~\ref{def:minbigulput} and \ref{def:minbigulget} respectively. Instead of using $v'$ in the $put$ direction like figures \ref{fig:eval-phead}, \ref{fig:eval-comp-phead} and \ref{fig:eval-comp-phead-2}, we just simply use notation $v$ as the updated view. The later definitions also follow this convention.
